---
title: 'Assignment V: GitHub and the ticketmaster.com API'
subtitle: 'Data Science Project Management | Winter Term 2021/22'
author: "Stefan Glaisner (4222790)"
date: "`r format(Sys.Date(), '%d-%m-%Y')`"
output:
  rmdformats::downcute:
    code_folding: hide
---

I hereby confirm that I worked on this Assignment entirely on my own and that my submission is in line with the *Code of Conduct* outlined on the lecture slides.

## 1. Setting up a new GitHub repository

Text


## 2. Getting to know the API

Text

```{r start, error = FALSE, warning = FALSE, message = FALSE}



```


## 3. Interacting with the API - the basics

Text

```{r start, error = FALSE, warning = FALSE, message = FALSE}



```


## 4. Interacting with the API - advanced

Text

```{r start, error = FALSE, warning = FALSE, message = FALSE}



```


## 5. Visualizing the extracted data

Text

```{r start, error = FALSE, warning = FALSE, message = FALSE}



```


## 6. Event locations in other countries

Text

```{r start, error = FALSE, warning = FALSE, message = FALSE}



```
